The 2- and 3-point surface correlation functions calculations: from novel exact continuous approach to improving methodology for discrete images

### 2023-05-17 paper.tex
Try to explain more about 'zero error'

We conclude that continuous approach has zero error against analytical solution
around can be used to assess the quality of digital approach for discretized
sets. As expected, digital approach performance depends on the image resolution
with new edge filter outperforming $H$.

@@

\subsection{Influence of filter $H'$ on computation accuracy}

\begin{figure*}
  \centering
  \subfigure[Surface-surface function calculated for a ball with radius
    $R = 0.24$. Image dimensions are  $450 \times 450 \times 450$.]{
    \includegraphics[width=0.3\linewidth]{images/ball-3d-ss.png}
    \label{fig:fss-ball}}
  \hfill
  \subfigure[Surface-void function calculated for a disk with radius
    $R = 0.2$. Image dimensions are $2000 \times 2000$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-disk.png}
    \label{fig:fsv-disk}}
  \hfill
  \subfigure[Surface-void function calculated for a ball with radius
    $R = 0.2$. Image dimensions are $300 \times 300 \times 300$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-ball.png}
    \label{fig:fsv-ball}}
  \caption[]{Comparison of filters $H$ and $H'$ for cases in which newly
    developed algorithms \cref{sec:fss-2d}, \cref{sec:fsss-3d} are not
    applicable. Theoretical curves are provided for each case.}
  \label{fig:not-covered}
\end{figure*}
With the new filter the calculation of $F_{ss}$ becomes more precise also for
three-dimensional images. This can be seen in comparison with theoretical values
for known cases, e.g., a ball. On \cref{fig:fss-ball} plots
of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
theoretical curve are presented. It can be verified that filter $H'$ is indeed results 
in higher accuracies with the help of error metric:
\begin{equation}
  error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
      F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
  \label{eq:error}
\end{equation}
where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
$\epsilon = 0.01$ we obtain the +$error = 0.05$ for filter $H$ and $error = 0.03$ for
filter $H'$, respectively. Calculation of surface-void function also benefits from the new
filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).

>>>>

We conclude that if a theoretical solution is known for the correlation function
$F_{ss}$ or $F_{sss}$, then evaluation of this function using our continuous
approach does not differ from this theoretical solution if all crossings of
the interface with its translated self are found correctly (which is the case
for all sets described in this paper). This approach can be used to assess the
quality of the algorithm for discretized sets. As expected, performance of the
latter depends on the image resolution and the choise of an edge detection
filter (the new filter $H'$ is preferable than $H$ for images with good
resolution, see \cref{sec:influence}).

@@

\subsection{Influence of filter $H'$ on computation accuracy}
\label{sec:influence}
\begin{figure*}
  \centering
  \subfigure[Surface-surface function calculated for a ball with radius
    $R = 0.24$. Image dimensions are  $450 \times 450 \times 450$.]{
    \includegraphics[width=0.3\linewidth]{images/ball-3d-ss.png}
    \label{fig:fss-ball}}
  \hfill
  \subfigure[Surface-void function calculated for a disk with radius
    $R = 0.2$. Image dimensions are $2000 \times 2000$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-disk.png}
    \label{fig:fsv-disk}}
  \hfill
  \subfigure[Surface-void function calculated for a ball with radius
    $R = 0.2$. Image dimensions are $300 \times 300 \times 300$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-ball.png}
    \label{fig:fsv-ball}}
  \caption[]{Comparison of filters $H$ and $H'$ for cases in which newly
    developed algorithms \cref{sec:fss-2d}, \cref{sec:fsss-3d} are not
    applicable. Theoretical curves are provided for each case.}
  \label{fig:not-covered}
\end{figure*}
With the new filter the calculation of $F_{ss}$ becomes more precise also for
three-dimensional images. This can be seen in comparison with theoretical values
for known cases, e.g., a ball. On \cref{fig:fss-ball} plots
of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
theoretical curve are presented. It can be verified that filter $H'$ is indeed results 
in higher accuracies with the help of error metric:
\begin{equation}
  error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
      F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
  \label{eq:error}
\end{equation}
where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
$\epsilon = 0.01$ we obtain the +$error = 0.05$ for filter $H$ and $error = 0.03$ for
filter $H'$, respectively. Calculation of surface-void function also benefits from the new
filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).
